cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Added subtitle for the second application
Added initial setup for five clusters data

@@

>>>>

```{r set-seed}
set.seed(20240412)
```

@@

```{r gen-five-clust-data}

positions <- geozoo::simplex(p=4)$points

## To generate data
five_clusts <- gen_multicluster(n = c(450, 300, 150, 250, 350), p = 4, k = 5,
                       loc = positions,
                       scale = c(0.4, 0.35, 0.3, 1, 0.3),
                       shape = c("helicalspiral", "hemisphere", "unifcube", "bluntedcone", "gaussian"),
                       rotation = NULL,
                       is_bkg = FALSE)
```

```{r}
langevitour::langevitour(five_clusts[, -5])
```

```{r projections}

## Assessing single and complete linkage in the presence of noise dimensions
